---
title: "Homework 1"
author: Kexin Sun
output: github_document
---

This is my solution to Homework 1.


```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)

```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))

```

I can take the mean of numbers and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))
```


```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df,factor_vec)) * pull(prob1_df, samp)

```



## Problem 2

Load the "penguins" dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

# Section 1
Short description of penguins dataset:

<<<<<<< HEAD
There are `r ncol(penguins)` variables and `r nrow(penguins)` observations in this data set,
and variables are "`r names(penguins)`".

For variable **species**, levels are `r levels(pull(penguins,species))`.

For variable **island**, levels are `r levels(pull(penguins,island))`.

For variable **bill_length_mm**, range is `r range(pull(penguins,bill_length_mm),na.rm = TRUE)`.

For variable **bill_depth_mm**, range is `r range(pull(penguins,bill_depth_mm),na.rm = TRUE)`.

For variable **flipper_length_mm**, range is `r range(pull(penguins,flipper_length_mm),na.rm = TRUE)`.

For variable **body_mass_g**, range is `r range(pull(penguins,body_mass_g),na.rm = TRUE)`.

For variable **year**, range is `r range(pull(penguins,year))`.

For variable **sex**, levels are `r levels(pull(penguins,sex))`.




```{r}
ncol(penguins)
nrow(penguins)
names(penguins)
levels(pull(penguins,species))
levels(pull(penguins,island))
range(pull(penguins,bill_length_mm),na.rm = TRUE)
range(pull(penguins,bill_depth_mm),na.rm = TRUE)
range(pull(penguins,flipper_length_mm),na.rm = TRUE)
range(pull(penguins,body_mass_g),na.rm = TRUE)
range(pull(penguins,year))
levels(pull(penguins,sex))

```



I also take the mean of flipper length, 
and it is `r mean(pull(penguins,flipper_length_mm),na.rm = TRUE)`.

```{r}
mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```


# Section 2
Scatter plot of flipper_length_mm (y) vs bill_length_mm (x) 

```{r}
plot_df = tibble(
  x = pull(penguins, bill_length_mm),
  y = pull(penguins, flipper_length_mm),
  species = pull(penguins, species)
)

ggplot(plot_df, aes(x = x, y = y, color = species)) + geom_point()
```

Export the ggplot

```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

